An Object-Logic Explanation for the Inconsistency in G\"odel's Ontological Theory

### 2016-07-11 Papers/2016/KI/main.tex
Compress Coq scripts and remove footnote.

The proofs above have been formalized and verified step-by-step in \textsc{Coq}\footnote{The complete formal proofs can be found in: \url{https://github.com/FormalTheology/GoedelGod}.}. The following \textsc{Coq} script shows the formalization of step 8 of the meta-logic proof.

@@

Due to a deliberate and disciplined use of only 
the simplest (and non-automatic) \textsc{Coq} tactics, 
there is a straightforward correspondence between the tactics used 
in the scripts above and the inference rules of the modal natural 
deduction calculus \cite{CSR}. Therefore, the lengths of the proof 
scripts (in number of tactic applications) can serve as estimations 
for the lengths of the corresponding natural deduction proof. 
It is noticeable that the meta-logic proof is significantly shorter 
than the pure object-logic proof. An in-depth analysis 
reveals that the reasoning about the possible worlds semantics in 
the meta-logic proof acts as a short-cut: when it becomes impossible (in step 8) to build the third world $w'$ (because $\bot$ would have to hold in it, and thus $w'$ would be contradictory), a contradiction at the HOL level can be immediately derived, completing the proof. In the object-level proof, on the other hand, such a contradiction had to be found in the arbitrary initial world $w$. This not only requires additional tedious logical inferences (cf. the proofs of the lemmas \texttt{mimplies\_to\_mnot} and \texttt{dia\_not\_not\_box}), but also a non-trivial guessing of the instantiating contradictory proposition $\pos \pos \bot$, whose purpose is precisely to carry over the contradiction from $w'$ back to $w$.

>>>>

The proofs above have been formalized and verified step-by-step in \textsc{Coq}. The complete proofs can be found in \url{https://github.com/FormalTheology/GoedelGod}. The following \textsc{Coq} script shows the formalization of step 8 of the meta-logic proof.

@@

\noindent
Due to a deliberate and disciplined use of only 
the simplest (and non-automatic) \textsc{Coq} tactics, 
there is a straightforward correspondence between the tactics used 
in the scripts above and the inference rules of the modal natural 
deduction calculus \cite{CSR}. Therefore, the lengths of the proof 
scripts (in number of tactic applications) can serve as estimations 
for the lengths of the corresponding natural deduction proof. 
It is noticeable that the meta-logic proof is significantly shorter 
than the pure object-logic proof. An in-depth analysis 
reveals that the reasoning about the possible worlds semantics in 
the meta-logic proof acts as a short-cut: when it becomes impossible (in step 8) to build the third world $w'$ (because $\bot$ would have to hold in it, and thus $w'$ would be contradictory), a contradiction at the HOL level can be immediately derived, completing the proof. In the object-level proof, on the other hand, such a contradiction had to be found in the arbitrary initial world $w$. This not only requires additional tedious logical inferences (cf. the proofs of the lemmas \texttt{mimplies\_to\_mnot} and \texttt{dia\_not\_not\_box}), but also a non-trivial guessing of the instantiating contradictory proposition $\pos \pos \bot$, whose purpose is precisely to carry over the contradiction from $w'$ back to $w$.
